Regularising Lotka--Volterra interaction matrices by species grouping: optimal groupings are unpredictable

### 2022-03-21 article.rnw
Remove an extraneous comma.

Coclassification matrices for the row and column groupings are shown in \cref{fig:coclassification}.
In all, no pair of species can confidently be said to be coclassified, in the row or column groupings; no probability of coclassification exceeded \SI{75}{\percent}.
Some pairs of species were far more likely to be coclassified than others, however, suggesting some structure to the best groupings.

>>>>

Coclassification matrices for the row and column groupings are shown in \cref{fig:coclassification}.
In all, no pair of species can confidently be said to be coclassified in the row or column groupings; no probability of coclassification exceeded \SI{75}{\percent}.
Some pairs of species were far more likely to be coclassified than others, however, suggesting some structure to the best groupings.
